Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-22 paper/ijcai/paper.tex
pass on 5.2

\subsection{Experimental Methodology}\label{sec:methodology}

\Fix{
To evaluate our approach, we compare the cost of diagnosing
a collection of faults using \sfl{} versus \comb{}.
}

To evaluate the effectiveness of \comb{}, following related work, we compared
its performance with \sfl{} for each fault from the dataset, for $k\in\{5,10\}$,
where $k$ is the number of classes comprising the highest faulty statements.
These classes are obtained directly from the ranking which is calculated through
\sfl{}. For each fault, spectra is updated and the fault ranking is
re-calculated but only considering the $k$ highest faulty classes. We refer to
these variations as SFL$^{k}$. After slicing each class of the top $k$ of the
highest faulty classes for each fault, the initial spectra is updated based on
the slicer output and the fault ranking is re-calculated. We refer to these
variations as \combpar{k}. We compared \combpar{5} and \combpar{10} against
\sfl{}$^{5}$ and \sfl{}$^{10}$ using the commonly used metric $\Delta{}C =
C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})$, where $C$ is the cost of
diagnosis. $C$ is the mean ranking of all buggy statements. $\Delta C >0$ means
that the position of the faulty statement has decreased in the ranking after
applying the \combpar{k} approach. Hence, reducing the cost of locating the bug.
$\Delta C <0$ means that the faulty statement may be removed by \combpar{k}.
$\Delta C=0$ means that the faulty statement remained in the same position.  We
also assume a perfect bug understanding, i.e., if the developer sees the bug in
the ranking, he can say it is the faulty one.

\subsection{Results and Discussion}

@@

In this section, we answer the research questions proposed and discuss the
results obtained. Our approach was capable of slicing a total of $260$ faults
from $5$ different  projects. The remaining faults were not considered because
(1) faults belong to the \closure{} project which requires high CPU to perform
the \combpar{k} evaluation  or (2) faults whose test outputs were not
reproducible in the machine used to run the experiments. \textbf{RQ1} evaluates how effective is \ds{} on reducing the test cases, \textbf{RQ2} reviews
one of the main issues of \ds{} - missing faulty statements - and
\textbf{RQ3} discusses how effective is the \combpar{k} approach against
\sfl{}$^{k}$.

@@

@@

\subsection{Threats to validity}
%
A potential threat to external validity related to the set of programs used in
our study. When choosing the projects for our study, our aim was to opt for
projects that resemble a general and large-sized application. To reduce
selection bias and facilitate the comparison of our results, we decided to
choose a benchmark that is popular in the community~\cite{just-defects4j-issta2014}.

>>>>

%\subsection{Experimental Methodology}
%\label{sec:methodology}

\subsection{Techniques}
One important independent variable for this study is the scope of
dynamic slicing. Slicing the entire code would be unacceptably
expensive as Critical Slicing needs to re-compile the affected file at
every iteration, \ie{}, after deleting statements and before checking
the oracle (see Section~\ref{sec:slicing}). We control the scope of
slicing through the variable $k$, which denotes the number of distinct
files that dynamic slicing will minimize. In this study, we used 5 and
10 as the values of $k$. The $k$ files for minimization are selected
from the \sfl{} ranking as follows. First, we build a rank of files by
determining, for each ranked statement, the file that declares
it. Then, we select the top $k$ distinct files from such file ranking.

The techniques we evaluate in this study are \combpar{k} and
SFL$^{k}$, which is the comparison baseline. \combpar{k} is as defined
in Section~\ref{sec:approach} (see Step 2 of the workflow) whereas
SFL$^{k}$ is as SFL, but it produces a ranking including exclusively
the statements from the best-$k$ ranked files.

%% To evaluate the effectiveness of \comb{}, following related work, we compared
%% its performance with \sfl{} for each fault from the dataset, for $k\in\{5,10\}$,
%% where $k$ is the number of classes comprising the highest faulty statements.
%% These classes are obtained directly from the ranking which is calculated through
%% \sfl{}.

%% For each fault, spectra is updated and the fault ranking is
%% re-calculated but only considering the $k$ highest faulty classes. We refer to
%% these variations as SFL$^{k}$. After slicing each class of the top $k$ of the
%% highest faulty classes for each fault, the initial spectra is updated based on
%% the slicer output and the fault ranking is re-calculated. We refer to these
%% variations as \combpar{k}.

\subsection{Results}

\Mar{--------------------------- estou aqui}

This section addresses the research questions we posed.

%% proposed and discuss the
%% results obtained. Our approach was capable of slicing a total of $260$ faults
%% from $5$ different  projects.
%% \textbf{RQ1} evaluates how effective is \ds{} on reducing the test cases, \textbf{RQ2} reviews
%% one of the main issues of \ds{} - missing faulty statements - and
%% \textbf{RQ3} discusses how effective is the \combpar{k} approach against
%% \sfl{}$^{k}$.

@@

@@

\Mar{metric only used here...revise}
\Fix{
We compared \combpar{5} and \combpar{10} against
\sfl{}$^{5}$ and \sfl{}$^{10}$ using the commonly used metric $\Delta{}C =
C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})$, where $C$ is the cost of
diagnosis. $C$ is the mean ranking of all buggy statements. $\Delta C >0$ means
that the position of the faulty statement has decreased in the ranking after
applying the \combpar{k} approach. Hence, reducing the cost of locating the bug.
$\Delta C <0$ means that the faulty statement may be removed by \combpar{k}.
$\Delta C=0$ means that the faulty statement remained in the same position.  We
also assume a perfect bug understanding, i.e., if the developer sees the bug in
the ranking, he can say it is the faulty one.
}

@@

\subsection{Threats to validity}

\Mar{incorporate this here. we were presenting this too early (initial
  par. of results). not very appealing ;)}
\Fix{
The remaining faults were not considered because
(1) faults belong to the \closure{} project which requires high CPU to perform
the \combpar{k} evaluation  or (2) faults whose test outputs were not
reproducible in the machine used to run the experiments.
}

%
A potential threat to external validity related to the set of programs used in
our study. When choosing the projects for our study, our aim was to opt for
projects that resemble a general and large-sized application. To reduce
selection bias and facilitate the comparison of our results, we decided to
choose a benchmark that is popular in the community~\cite{just-defects4j-issta2014}.
